Apparent preferences for cognitive effort fade when multiple forms of effort

### 2021-04-15 Manuscript.Rmd
cleaner headers and removal of new summarise() warnings (thanks tidyverse...)

@@

# Proportion of performance-based forced travels per subject and cost type
# move to 16.2.1.
propFails <- dataBtw %>% 
  filter(Cost != "Wait") %>% 
  group_by(SubjID, Cost) %>% 
  summarise(propFails = mean(rawChoice == 2)) %>%
  group_by(Cost) %>% 
  summarise(meanFT = mean(propFails),
            sdFT = sd(propFails))
```

@@

``` {r BTW: 16.1.3. Earnings, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
## calculate the proportions and earnings per subject, while keeping group info
temp <- dataBtw %>%
  filter(rawChoice < 2) %>%
  group_by(SubjID, Cost) %>%
  summarise(Earnings = sum(Offer[Choice == 1] / 100),
            pComplete = mean(Choice)) %>%
  mutate(pComplete2 = pComplete^2) %>%
  ungroup()

@@

## if you want to replicate the cost 3 method
# this says that all but easy deviated from optimality in the observed direction
temp <- dataBtw %>%
  group_by(Cost) %>%
  filter(Offer < 20) %>%
  summarize(propAccept = mean(Choice),
            accept = sum(Choice),
            quit = sum(Choice == 0))

@@

``` {r BTW: 16.2.1. Overall Proportion/Earnings, fig.align = "center", fig.width = 8, fig.height = 4, echo = FALSE}  
## earnings and proportion accepted per cost type
# note that earnings are based on successful completions, not just acceptances
temp <- dataBtw %>%
        group_by(SubjID, Cost) %>%
        summarise(Earnings = sum(Offer[(Choice == 1) & (rawChoice < 2)] / 100),
                  pAccept = mean(Choice))

## summaries
overallSumms <- temp %>% 
  group_by(Cost) %>% 
  summarise (mProp = mean(pAccept), 
             sdProp = sd(pAccept), 
             mEarn = mean(Earnings), 
             sdEarn = sd(Earnings)) %>%
  mutate_if(is.numeric, round, digits = 2)

@@

# and plot
hrPlot_btw <- dataBtw %>%
        filter(Choice < 2, Cost != "Easy") %>%
        group_by(SubjID, Cost, Handling, Offer, optimal) %>%
        summarise(pAccept = mean(Choice)) %>%
        group_by(Cost, Handling, Offer, optimal) %>%
        summarise(meanComplete = mean(pAccept),
                  SE = sd(pAccept) / sqrt(length(pAccept))) %>%
   ggplot(aes(interaction(Offer, Handling), meanComplete, color = Cost)) + 
        geom_point(size = 3) + 
        geom_errorbar(aes(ymin = meanComplete - SE, ymax = meanComplete + SE), width = 0.2, size = 1) +
        geom_line(aes(group = interaction(Handling, Cost)), size = 1) +
        geom_point(aes(y = round(optimal)), shape = 21, fill = "grey75", color = "grey30", size = 3, show.legend = F) +
        labs(x = "Offer.Handling", y = "Proportion Accepted") +
        scale_color_manual(values = colsBtw) +
        theme(legend.key = element_blank(),
              panel.grid.major = element_blank(), 
              panel.grid.minor = element_blank(), 
              panel.background = element_blank(), 
              axis.line = element_line(colour = "black"),
              text = element_text(size = 12))

@@

``` {r BTW: 16.2.3. Mixed Effects Model, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 4, include = FALSE}
# clean the data so the total acceptances and quits per subj x handling x reward are ready for modeling
mixLogis_main_btw <- list()
mixData <- dataBtw %>%
  #filter(Choice < 2) %>% analysis performed on acceptances, not completions
  group_by(SubjID, Cost, Handling, Offer) %>%
  summarize(totalChoices = length(Choice),
            totalAccepted = sum(Choice),
            totalQuits = sum(Choice == 0),
            propAccepted = mean(Choice)) %>%
  ungroup()

@@

# actual proportion of quits that happened after 1 s (i.e. after the grace period for physical)
handlingQuits_btw <- dataBtw %>%
  filter(rawChoice == 0) %>%
  summarize(r = round(mean(RT > 1.05), digits = 2)) # to account for some measurement error for the grace perior during grip

@@

## PRE/POST PAIRED PERMUTATIONS
temp <- dataBtw %>%
  group_by(SubjID, Cost) %>%
  summarise(propAccept_1 = mean(Choice[Half == "Half_1"]),
            propAccept_2 = mean(Choice[Half == "Half_2"])) %>%
  plyr::dlply("Cost", identity)

@@

``` {r BTW: 16.3.2. Plot Pre/Post, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
# scatter plot of pre/post acceptances
# first calculate the mean acceptances per cost/half to draw horizontal and vertical lines on the plot
df_mean <- dataBtw %>%
            group_by(SubjID, Cost, Block, Half) %>%
            summarise(propAccept = mean(Choice)) %>%
            group_by(SubjID, Cost, Half) %>%
            summarise(propAccept = mean(propAccept)) %>%
            spread(Half, propAccept) %>%
            group_by(Cost) %>%
            summarise(propAccept_1 = mean(Half_1),
                      propAccept_2 = mean(Half_2))

# and plot
prepost_btw$scatterplot <- dataBtw %>%
                        filter(Choice < 2) %>%
                        group_by(SubjID, Cost) %>%
                        summarise(propAccept_1 = mean(Choice[Half == "Half_1"]),
                                  propAccept_2 = mean(Choice[Half == "Half_2"])) %>%
                        ggplot(aes(propAccept_1, propAccept_2, fill = Cost)) +
                          geom_point(size = 3, pch = 21, color = "black", show.legend = F) +
                          scale_fill_manual(values = colsBtw) +
                          scale_color_manual(values = colsBtw) +
                          xlim(0, 1) +
                          ylim(0, 1) +
                          labs(x = "Proportion Accepted - 1st Half", y = "Proportion Accepted - 2nd Half") +
                          geom_abline(slope = 1, intercept = 0, lty = 2) +
                          geom_hline(data = df_mean, aes(yintercept = propAccept_2, color = Cost), linetype="dashed", show.legend = F) +
                          geom_vline(data = df_mean, aes(xintercept = propAccept_1, color = Cost), linetype="dashed", show.legend = F) +
                          theme(panel.grid.major = element_blank(),
                                panel.grid.minor = element_blank(),
                                panel.background = element_blank(),
                                axis.line = element_line(colour = "black"),
                                text = element_text(size = 14))

# acceptances per cost across blocks
# note that because the same handling/travel time combos repeat in the same order pre/post, 1/4-2/4-3/6 are direct comparisons
prepost_btw$propBlocks <- dataBtw %>%
                         filter(Choice < 2) %>%
                         group_by(SubjID, Cost, Block) %>%
                         summarise(propAccept_subj = mean(Choice)) %>%
                         group_by(Cost, Block) %>%
                         summarize(propAccept = mean(propAccept_subj),
                                   seAccept = sd(propAccept_subj)/sqrt(length(propAccept_subj))) %>%
                         ggplot(aes(Block, propAccept, color = Cost)) +
                           geom_vline(xintercept = 3.5, linetype = "dashed") +
                           geom_point(size = 2) +
                           geom_errorbar(aes(ymin = propAccept - seAccept, ymax = propAccept + seAccept, color = Cost), width = 0.1) +
                           geom_line() +
                           ylim(0, 1) +
                           labs(y = "Proportion Acccepted") +
                           scale_x_continuous(breaks = seq(6)) +
                           scale_color_manual(values = colsBtw) +
                           scale_fill_manual(values = colsBtw) +
                           theme(legend.key = element_blank(),
                                 legend.position = c(0.8, 0.3),
                                 panel.grid.major = element_blank(),
                                 panel.grid.minor = element_blank(),
                                 panel.background = element_blank(),
                                 axis.line = element_line(colour = "black"),
                                 text = element_text(size = 14))

# RTs for the cognitive tasks as a function of handling time, offer, and experimental half
prepost_btw$cogtaskRTs <- dataBtw_coglogs %>%
  filter(Choice == 1,
         Handling > 2) %>%
  group_by(SubjID, Handling, Offer, Trial_Time, Half) %>%
  summarise(mRT = mean(Task.RT)) %>%
  group_by(Handling, Offer, Trial_Time, Half) %>%
  summarise(meanRT = mean(mRT),
            seRT = sd(mRT, na.rm = T) / sqrt(21)) %>%
  ungroup() %>%
  mutate(Offer = factor(Offer, levels = c(4, 8, 20))) %>% 
  ggplot(aes(Trial_Time, meanRT, group = Offer, color = Offer)) +
    geom_line() +
    geom_line(aes(Trial_Time, meanRT + seRT, group = Offer, color = Offer), linetype = "dashed") +
    geom_line(aes(Trial_Time, meanRT - seRT, group = Offer, color = Offer), linetype = "dashed") +
    geom_point(size = 2) +
    ylim(0.2, 1) +
    facet_wrap(vars(Handling, Half)) +
    theme_classic()

@@

``` {r BTW: 16.3.2. Plot Pre/Post reward x handling, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
# this plot divides the proportion of acceptances for each reward/handling combination per half of the experiment
hrprepostPlot_btw <- dataBtw %>%
  group_by(SubjID) %>%
  mutate(Half = ifelse(Half == "Half_1", "First Half", "Second Half"),
         Handling = case_when(
           Handling == 2 ~ "2 s",
           Handling == 10 ~ "10 s",
           Handling == 14 ~ "14 s"
         ),
         Handling = factor(Handling, levels = c("2 s", "10 s", "14 s"))) %>%
  group_by(SubjID, Half, Handling, Cost, Offer) %>%
  summarise(pAccept = mean(Choice)) %>%
  group_by(Half, Cost, Handling, Offer) %>%
  summarise(propAccept = mean(pAccept),
            SE = sd(pAccept) / sqrt(length(pAccept))) %>%
  ungroup() %>%
  mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%  
  ggplot(aes(Offer, propAccept, color = Cost)) +
  geom_point(size = 1.2, show.legend = T) +
  geom_line(size = 0.8, show.legend = F) +
  scale_color_manual(values = colsBtw) +
  scale_fill_manual(values = colsBtw) +
  geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 0.8, show.legend = T) +
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
  scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
  labs(y = "Proportion Accepted") +
  facet_grid(Handling ~ Half) +
  theme_minimal(base_size = 20) +
  theme(legend.position = "bottom", 
        legend.margin=margin(t = -0.6, unit='cm'),
        strip.text.x = element_blank())

@@

``` {r BTW: 16.3.2. mix pre/post separately, echo = FALSE, fig.align="center", fig.width = 5, fig.height = 4}
## compute the same mixed effects logistic for each half
# mixed logistic for the first half
mixLogis_pre_btw <- list()
mixData <- dataBtw %>%
  filter(Half == "Half_1") %>%
  group_by(SubjID, Cost, Handling, Offer) %>%
  summarize(totalChoices = length(Choice),
            totalAccepted = sum(Choice),
            totalQuits = sum(Choice == 0),
            propAccepted = mean(Choice))

@@

# mixed logistic for the second half
mixLogis_post_btw <- list()
mixData <- dataBtw %>%
  filter(Half == "Half_2") %>%
  group_by(SubjID, Cost, Handling, Offer) %>%
  summarize(totalChoices = length(Choice),
            totalAccepted = sum(Choice),
            totalQuits = sum(Choice == 0),
            propAccepted = mean(Choice))

@@

# Summarize
baseCoeffs <- as.data.frame(t(sapply(logisticFits_base, "[[", "coefficients")))
baseCoeffs$ConvIters <- sapply(logisticFits_base, function(x) {summary(x)$iter})
baseCoeffs$R2 <- sapply(logisticFits_base, function(x) {1 - (summary(x)$deviance / summary(x)$null.deviance)})
baseCoeffs$aic <- sapply(logisticFits_base, function(x) {summary(x)$aic})
baseCoeffs$propAccept_total <- sapply(dataList, function(data) {mean(data$Choice)})
baseCoeffs$propAccept_totalSQRD <- baseCoeffs$propAccept_total^2
baseCoeffs$totalEarned <- (dataWth %>% group_by(SubjID) %>% summarize(totalEarned = sum(Offer[Choice == 1])))$totalEarned
baseCoeffs$SubjID <- subjList_wth # add subject list column to join the demographics by it below

@@

``` {r WTH: 16.1.3. prop accept x earnings, echo = FALSE, include = T, fig.align="center",fig.width = 4, fig.height = 4}
# Notes: I also performed this comparing halves and block types x half, and it doesn't look like participants were accepting less to make more.
# calculate the proportions and earnings per subject, while keeping group info
temp <- dataWth %>%
  filter(rawChoice < 2) %>%
  group_by(SubjID) %>%
  summarise(Earnings = sum(Offer[Choice == 1] / 100),
            pComplete = mean(Choice)) %>%
  mutate(pComplete2 = pComplete^2) %>%
  ungroup()

@@

``` {r WTH: 16.1.4. optimality, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
# get quits and acceptances per cost type 
temp <- dataWth %>%
  group_by(Cost) %>%
  filter(Offer < 20) %>%
  summarize(propAccept = mean(Choice),
            accept = sum(Choice),
            quit = sum(Choice == 0))

@@

## no differences in earnings
earnings_within <- dataWth %>%
  group_by(SubjID, Cost) %>%
  filter(rawChoice == 1) %>%
  summarise(earning = sum(Offer) / 100) %>%
  group_by(Cost) %>%
  summarise(mEarn = mean(earning),
            sdEarn = sd(earning)) %>%
  mutate_if(is.numeric, round, digits = 2)

@@

# mixed effects logistics, rotating the reference cost condition
mixLogis_main_wth <- list()
mixData <- dataWth %>%
  group_by(SubjID, Cost, Offer) %>%
  summarize(totalChoices = length(Choice),
            totalAccepted = sum(Choice),
            totalQuits = sum(Choice == 0),
            propAccepted = mean(Choice))

@@

# plot proportion accepted per trial/offer combo
hrPlot_wth <- dataWth %>%
        filter(Choice < 2) %>%
        group_by(Cost, Offer) %>%
        summarise(propAccept = mean(Choice),
                  SE = sd(Choice) / sqrt(nSubjs_wth)) %>%
        ungroup() %>%
        mutate(Optimal = rep(c(0, 1, 1), length(unique(dataWth$Cost))),
               #BlockType = as.factor(rep(c(0,1,0,1), each = 3)),
               Offer = ifelse(Offer == 20, 12, Offer)) %>%
        ggplot(aes(Offer, propAccept, color = Cost)) +
          geom_point(size = 3, show.legend = T) +
          geom_point(aes(y = Optimal), size = 3, pch = 21, fill = "grey75", color = "grey30") +
          geom_line(lwd = 1, show.legend = T) +
          scale_color_manual(values = colsWth) +
          scale_fill_manual(values = colsWth) +
          geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.4, size = 1) +
          scale_y_continuous(limits = c(0, 1), breaks = c(0,0.5,1)) +
          scale_x_continuous(breaks = c(4, 8, 12), labels = c("4", "8", "20")) +
          labs(y = "Proportion Accepted") +
          theme(legend.position = c(0.8, 0.25),
                legend.key = element_blank(),
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(),
                panel.background = element_blank(),
                axis.line = element_line(colour = "black"),
                text = element_text(size = 22))

@@

``` {r WTH: 16.3.2. quits in offer vs handling, echo = FALSE}
# Proportion of forced travels per subject and cost type
propFails_wth <- dataWth %>%
  filter(!Cost %in% c("Wait-C", "Wait-P")) %>%
  group_by(SubjID, Cost) %>%
  summarise(propFails = mean(rawChoice == 2) * 100)

# Proportion of quits once the trial started per subject
# ResponseType distinguished between offer quits and handling quits
propQuits_wth <- dataWth %>%
  filter(!(ResponseType %in% c("Forced Travel", "Forced travel", "Reward"))) %>%
  group_by(SubjID) %>%
  summarise(propAccept = mean(ResponseType == "Quit") * 100)

@@

## paired tests for first versus last block per cost type
## PRE/POST PAIRED PERMUTATIONS
temp <- dataWth %>%
  filter(!(Block %in% c(3, 4))) %>%
  group_by(SubjID, Cost) %>%
  summarise(propAccept_1 = mean(Choice[Half == "Half_1"]),
            propAccept_2 = mean(Choice[Half == "Half_2"])) %>%
  plyr::dlply("Cost", identity)

@@

# correlation between the difference in acceptance rates and mistakes
accDiff <- dataWth %>%
  filter(!(Block %in% c(3, 4)), 
         Cost %in% c("Cognitive", "Physical")) %>%
  group_by(SubjID, Cost) %>%
  summarise(propAccept_1 = mean(Choice[Half == "Half_1"]),
            propAccept_2 = mean(Choice[Half == "Half_2"])) %>%
  mutate(Diff = propAccept_2 - propAccept_1)

@@

# no differences in forced travels across halves
temp <- dataWth %>%
  filter(!Cost %in% c("Wait-C", "Wait-P")) %>%
  group_by(SubjID,  Half) %>%
  summarise(propFails = mean(rawChoice == 2)) %>%
  spread(Half, propFails)

>>>>

&nbsp;

@@

# Proportion of performance-based forced travels per subject and cost type
# move to 16.2.1.
propFails <- dataBtw %>% 
  filter(Cost != "Wait") %>% 
  group_by(SubjID, Cost) %>% 
  summarise(propFails = mean(rawChoice == 2), .groups = 'drop') %>%
  group_by(Cost) %>% 
  summarise(meanFT = mean(propFails),
            sdFT = sd(propFails), .groups = 'drop')
```

@@

``` {r BTW: 16.1.3. Earnings, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
## calculate the proportions and earnings per subject, while keeping group info
temp <- dataBtw %>%
  filter(rawChoice < 2) %>%
  group_by(SubjID, Cost) %>%
  summarise(Earnings = sum(Offer[Choice == 1] / 100),
            pComplete = mean(Choice), .groups = 'drop') %>%
  mutate(pComplete2 = pComplete^2) %>%
  ungroup()

@@

## if you want to replicate the cost 3 method
# this says that all but easy deviated from optimality in the observed direction
temp <- dataBtw %>%
  group_by(Cost) %>%
  filter(Offer < 20) %>%
  summarize(propAccept = mean(Choice),
            accept = sum(Choice),
            quit = sum(Choice == 0), .groups = 'drop')

@@

``` {r BTW: 16.2.1. Overall Proportion/Earnings, fig.align = "center", fig.width = 8, fig.height = 4, echo = FALSE}  
## earnings and proportion accepted per cost type
# note that earnings are based on successful completions, not just acceptances
temp <- dataBtw %>%
        group_by(SubjID, Cost) %>%
        summarise(Earnings = sum(Offer[(Choice == 1) & (rawChoice < 2)] / 100),
                  pAccept = mean(Choice), .groups = 'drop')

## summaries
overallSumms <- temp %>% 
  group_by(Cost) %>% 
  summarise(mProp = mean(pAccept), 
             sdProp = sd(pAccept), 
             mEarn = mean(Earnings), 
             sdEarn = sd(Earnings), .groups = 'drop') %>%
  mutate_if(is.numeric, round, digits = 2)

@@

# and plot
hrPlot_btw <- dataBtw %>%
        filter(Choice < 2, Cost != "Easy") %>%
        group_by(SubjID, Cost, Handling, Offer, optimal) %>%
        summarise(pAccept = mean(Choice), .groups = 'drop') %>%
        group_by(Cost, Handling, Offer, optimal) %>%
        summarise(meanComplete = mean(pAccept),
                  SE = sd(pAccept) / sqrt(length(pAccept)), .groups = 'drop') %>%
   ggplot(aes(interaction(Offer, Handling), meanComplete, color = Cost)) + 
        geom_point(size = 3) + 
        geom_errorbar(aes(ymin = meanComplete - SE, ymax = meanComplete + SE), width = 0.2, size = 1) +
        geom_line(aes(group = interaction(Handling, Cost)), size = 1) +
        geom_point(aes(y = round(optimal)), shape = 21, fill = "grey75", color = "grey30", size = 3, show.legend = F) +
        labs(x = "Offer.Handling", y = "Proportion Accepted") +
        scale_color_manual(values = colsBtw) +
        theme(legend.key = element_blank(),
              panel.grid.major = element_blank(), 
              panel.grid.minor = element_blank(), 
              panel.background = element_blank(), 
              axis.line = element_line(colour = "black"),
              text = element_text(size = 12))

@@

``` {r BTW: 16.2.3. Mixed Effects Model, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 4, include = FALSE}
# clean the data so the total acceptances and quits per subj x handling x reward are ready for modeling
mixLogis_main_btw <- list()
mixData <- dataBtw %>%
  #filter(Choice < 2) %>% analysis performed on acceptances, not completions
  group_by(SubjID, Cost, Handling, Offer) %>%
  summarize(totalChoices = length(Choice),
            totalAccepted = sum(Choice),
            totalQuits = sum(Choice == 0),
            propAccepted = mean(Choice), .groups = 'drop') %>%
  ungroup()

@@

# actual proportion of quits that happened after 1 s (i.e. after the grace period for physical)
handlingQuits_btw <- dataBtw %>%
  filter(rawChoice == 0) %>%
  summarize(r = round(mean(RT > 1.05), digits = 2), .groups = 'drop') # to account for some measurement error for the grace perior during grip

@@

## PRE/POST PAIRED PERMUTATIONS
temp <- dataBtw %>%
  group_by(SubjID, Cost) %>%
  summarise(propAccept_1 = mean(Choice[Half == "Half_1"]),
            propAccept_2 = mean(Choice[Half == "Half_2"]), .groups = 'drop') %>%
  plyr::dlply("Cost", identity)

@@

``` {r BTW: 16.3.2. Plot Pre/Post, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
# scatter plot of pre/post acceptances
# first calculate the mean acceptances per cost/half to draw horizontal and vertical lines on the plot
df_mean <- dataBtw %>%
            group_by(SubjID, Cost, Block, Half) %>%
            summarise(propAccept = mean(Choice), .groups = 'drop') %>%
            group_by(SubjID, Cost, Half) %>%
            summarise(propAccept = mean(propAccept), .groups = 'drop') %>%
            spread(Half, propAccept) %>%
            group_by(Cost) %>%
            summarise(propAccept_1 = mean(Half_1),
                      propAccept_2 = mean(Half_2), .groups = 'drop')

# and plot
prepost_btw$scatterplot <- dataBtw %>%
                        filter(Choice < 2) %>%
                        group_by(SubjID, Cost) %>%
                        summarise(propAccept_1 = mean(Choice[Half == "Half_1"]),
                                  propAccept_2 = mean(Choice[Half == "Half_2"]), .groups = 'drop') %>%
                        ggplot(aes(propAccept_1, propAccept_2, fill = Cost)) +
                          geom_point(size = 3, pch = 21, color = "black", show.legend = F) +
                          scale_fill_manual(values = colsBtw) +
                          scale_color_manual(values = colsBtw) +
                          xlim(0, 1) +
                          ylim(0, 1) +
                          labs(x = "Proportion Accepted - 1st Half", y = "Proportion Accepted - 2nd Half") +
                          geom_abline(slope = 1, intercept = 0, lty = 2) +
                          geom_hline(data = df_mean, aes(yintercept = propAccept_2, color = Cost), linetype="dashed", show.legend = F) +
                          geom_vline(data = df_mean, aes(xintercept = propAccept_1, color = Cost), linetype="dashed", show.legend = F) +
                          theme(panel.grid.major = element_blank(),
                                panel.grid.minor = element_blank(),
                                panel.background = element_blank(),
                                axis.line = element_line(colour = "black"),
                                text = element_text(size = 14))

# acceptances per cost across blocks
# note that because the same handling/travel time combos repeat in the same order pre/post, 1/4-2/4-3/6 are direct comparisons
prepost_btw$propBlocks <- dataBtw %>%
                         filter(Choice < 2) %>%
                         group_by(SubjID, Cost, Block) %>%
                         summarise(propAccept_subj = mean(Choice), .groups = 'drop') %>%
                         group_by(Cost, Block) %>%
                         summarize(propAccept = mean(propAccept_subj),
                                   seAccept = sd(propAccept_subj)/sqrt(length(propAccept_subj)), .groups = 'drop') %>%
                         ggplot(aes(Block, propAccept, color = Cost)) +
                           geom_vline(xintercept = 3.5, linetype = "dashed") +
                           geom_point(size = 2) +
                           geom_errorbar(aes(ymin = propAccept - seAccept, ymax = propAccept + seAccept, color = Cost), width = 0.1) +
                           geom_line() +
                           ylim(0, 1) +
                           labs(y = "Proportion Acccepted") +
                           scale_x_continuous(breaks = seq(6)) +
                           scale_color_manual(values = colsBtw) +
                           scale_fill_manual(values = colsBtw) +
                           theme(legend.key = element_blank(),
                                 legend.position = c(0.8, 0.3),
                                 panel.grid.major = element_blank(),
                                 panel.grid.minor = element_blank(),
                                 panel.background = element_blank(),
                                 axis.line = element_line(colour = "black"),
                                 text = element_text(size = 14))

# RTs for the cognitive tasks as a function of handling time, offer, and experimental half
prepost_btw$cogtaskRTs <- dataBtw_coglogs %>%
  filter(Choice == 1,
         Handling > 2) %>%
  group_by(SubjID, Handling, Offer, Trial_Time, Half) %>%
  summarise(mRT = mean(Task.RT), .groups = 'drop') %>%
  group_by(Handling, Offer, Trial_Time, Half) %>%
  summarise(meanRT = mean(mRT),
            seRT = sd(mRT, na.rm = T) / sqrt(21), .groups = 'drop') %>%
  ungroup() %>%
  mutate(Offer = factor(Offer, levels = c(4, 8, 20))) %>% 
  ggplot(aes(Trial_Time, meanRT, group = Offer, color = Offer)) +
    geom_line() +
    geom_line(aes(Trial_Time, meanRT + seRT, group = Offer, color = Offer), linetype = "dashed") +
    geom_line(aes(Trial_Time, meanRT - seRT, group = Offer, color = Offer), linetype = "dashed") +
    geom_point(size = 2) +
    ylim(0.2, 1) +
    facet_wrap(vars(Handling, Half)) +
    theme_classic()

@@

``` {r BTW: 16.3.2. Plot Pre/Post reward x handling, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
# this plot divides the proportion of acceptances for each reward/handling combination per half of the experiment
hrprepostPlot_btw <- dataBtw %>%
  group_by(SubjID) %>%
  mutate(Half = ifelse(Half == "Half_1", "First Half", "Second Half"),
         Handling = case_when(
           Handling == 2 ~ "2 s",
           Handling == 10 ~ "10 s",
           Handling == 14 ~ "14 s"
         ),
         Handling = factor(Handling, levels = c("2 s", "10 s", "14 s"))) %>%
  group_by(SubjID, Half, Handling, Cost, Offer) %>%
  summarise(pAccept = mean(Choice), .groups = 'drop') %>%
  group_by(Half, Cost, Handling, Offer) %>%
  summarise(propAccept = mean(pAccept),
            SE = sd(pAccept) / sqrt(length(pAccept)), .groups = 'drop') %>%
  ungroup() %>%
  mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%  
  ggplot(aes(Offer, propAccept, color = Cost)) +
  geom_point(size = 1.2, show.legend = T) +
  geom_line(size = 0.8, show.legend = F) +
  scale_color_manual(values = colsBtw) +
  scale_fill_manual(values = colsBtw) +
  geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 0.8, show.legend = T) +
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
  scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
  labs(y = "Proportion Accepted") +
  facet_grid(Handling ~ Half) +
  theme_minimal(base_size = 20) +
  theme(legend.position = "bottom", 
        legend.margin=margin(t = -0.6, unit='cm'),
        strip.text.x = element_blank())

@@

``` {r BTW: 16.3.2. mix pre/post separately, echo = FALSE, fig.align="center", fig.width = 5, fig.height = 4}
## compute the same mixed effects logistic for each half
# mixed logistic for the first half
mixLogis_pre_btw <- list()
mixData <- dataBtw %>%
  filter(Half == "Half_1") %>%
  group_by(SubjID, Cost, Handling, Offer) %>%
  summarize(totalChoices = length(Choice),
            totalAccepted = sum(Choice),
            totalQuits = sum(Choice == 0),
            propAccepted = mean(Choice), .groups = 'drop')

@@

# mixed logistic for the second half
mixLogis_post_btw <- list()
mixData <- dataBtw %>%
  filter(Half == "Half_2") %>%
  group_by(SubjID, Cost, Handling, Offer) %>%
  summarize(totalChoices = length(Choice),
            totalAccepted = sum(Choice),
            totalQuits = sum(Choice == 0),
            propAccepted = mean(Choice), .groups = 'drop')

@@

# Summarize
baseCoeffs <- as.data.frame(t(sapply(logisticFits_base, "[[", "coefficients")))
baseCoeffs$ConvIters <- sapply(logisticFits_base, function(x) {summary(x)$iter})
baseCoeffs$R2 <- sapply(logisticFits_base, function(x) {1 - (summary(x)$deviance / summary(x)$null.deviance)})
baseCoeffs$aic <- sapply(logisticFits_base, function(x) {summary(x)$aic})
baseCoeffs$propAccept_total <- sapply(dataList, function(data) {mean(data$Choice)})
baseCoeffs$propAccept_totalSQRD <- baseCoeffs$propAccept_total^2
baseCoeffs$totalEarned <- (dataWth %>% group_by(SubjID) %>% summarize(totalEarned = sum(Offer[Choice == 1]), .groups = 'drop'))$totalEarned
baseCoeffs$SubjID <- subjList_wth # add subject list column to join the demographics by it below

@@

``` {r WTH: 16.1.3. prop accept x earnings, echo = FALSE, include = T, fig.align="center",fig.width = 4, fig.height = 4}
# Notes: I also performed this comparing halves and block types x half, and it doesn't look like participants were accepting less to make more.
# calculate the proportions and earnings per subject, while keeping group info
temp <- dataWth %>%
  filter(rawChoice < 2) %>%
  group_by(SubjID) %>%
  summarise(Earnings = sum(Offer[Choice == 1] / 100),
            pComplete = mean(Choice), .groups = 'drop') %>%
  mutate(pComplete2 = pComplete^2) %>%
  ungroup()

@@

``` {r WTH: 16.1.4. optimality, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
# get quits and acceptances per cost type 
temp <- dataWth %>%
  group_by(Cost) %>%
  filter(Offer < 20) %>%
  summarize(propAccept = mean(Choice),
            accept = sum(Choice),
            quit = sum(Choice == 0), .groups = 'drop')

@@

## no differences in earnings
earnings_within <- dataWth %>%
  group_by(SubjID, Cost) %>%
  filter(rawChoice == 1) %>%
  summarise(earning = sum(Offer) / 100, .groups = 'drop') %>%
  group_by(Cost) %>%
  summarise(mEarn = mean(earning),
            sdEarn = sd(earning), .groups = 'drop') %>%
  mutate_if(is.numeric, round, digits = 2)

@@

# mixed effects logistics, rotating the reference cost condition
mixLogis_main_wth <- list()
mixData <- dataWth %>%
  group_by(SubjID, Cost, Offer) %>%
  summarize(totalChoices = length(Choice),
            totalAccepted = sum(Choice),
            totalQuits = sum(Choice == 0),
            propAccepted = mean(Choice), .groups = 'drop')

@@

# plot proportion accepted per trial/offer combo
hrPlot_wth <- dataWth %>%
        filter(Choice < 2) %>%
        group_by(Cost, Offer) %>%
        summarise(propAccept = mean(Choice),
                  SE = sd(Choice) / sqrt(nSubjs_wth), .groups = 'drop') %>%
        ungroup() %>%
        mutate(Optimal = rep(c(0, 1, 1), length(unique(dataWth$Cost))),
               #BlockType = as.factor(rep(c(0,1,0,1), each = 3)),
               Offer = ifelse(Offer == 20, 12, Offer)) %>%
        ggplot(aes(Offer, propAccept, color = Cost)) +
          geom_point(size = 3, show.legend = T) +
          geom_point(aes(y = Optimal), size = 3, pch = 21, fill = "grey75", color = "grey30") +
          geom_line(lwd = 1, show.legend = T) +
          scale_color_manual(values = colsWth) +
          scale_fill_manual(values = colsWth) +
          geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.4, size = 1) +
          scale_y_continuous(limits = c(0, 1), breaks = c(0,0.5,1)) +
          scale_x_continuous(breaks = c(4, 8, 12), labels = c("4", "8", "20")) +
          labs(y = "Proportion Accepted") +
          theme(legend.position = c(0.8, 0.25),
                legend.key = element_blank(),
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(),
                panel.background = element_blank(),
                axis.line = element_line(colour = "black"),
                text = element_text(size = 22))

@@

``` {r WTH: 16.3.2. quits in offer vs handling, echo = FALSE}
# Proportion of forced travels per subject and cost type
propFails_wth <- dataWth %>%
  filter(!Cost %in% c("Wait-C", "Wait-P")) %>%
  group_by(SubjID, Cost) %>%
  summarise(propFails = mean(rawChoice == 2) * 100, .groups = 'drop')

# Proportion of quits once the trial started per subject
# ResponseType distinguished between offer quits and handling quits
propQuits_wth <- dataWth %>%
  filter(!(ResponseType %in% c("Forced Travel", "Forced travel", "Reward"))) %>%
  group_by(SubjID) %>%
  summarise(propAccept = mean(ResponseType == "Quit") * 100, .groups = 'drop')

@@

## paired tests for first versus last block per cost type
## PRE/POST PAIRED PERMUTATIONS
temp <- dataWth %>%
  filter(!(Block %in% c(3, 4))) %>%
  group_by(SubjID, Cost) %>%
  summarise(propAccept_1 = mean(Choice[Half == "Half_1"]),
            propAccept_2 = mean(Choice[Half == "Half_2"]), .groups = 'drop') %>%
  plyr::dlply("Cost", identity)

@@

# correlation between the difference in acceptance rates and mistakes
accDiff <- dataWth %>%
  filter(!(Block %in% c(3, 4)), 
         Cost %in% c("Cognitive", "Physical")) %>%
  group_by(SubjID, Cost) %>%
  summarise(propAccept_1 = mean(Choice[Half == "Half_1"]),
            propAccept_2 = mean(Choice[Half == "Half_2"]), .groups = 'drop') %>%
  mutate(Diff = propAccept_2 - propAccept_1)

@@

# no differences in forced travels across halves
temp <- dataWth %>%
  filter(!Cost %in% c("Wait-C", "Wait-P")) %>%
  group_by(SubjID,  Half) %>%
  summarise(propFails = mean(rawChoice == 2), .groups = 'drop') %>%
  spread(Half, propFails)
